Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-29 paper_comparison/paper_comparison/paper_comparison.Rmd
Fix the caption for power cmp

```{r polypower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for non-linear patterns (uniform fitted values only). Main plot shows the power curves estimated using logistic regression, with dots indicating human evaluations of lineups. Surrounding band of the visual test shows the 95 percent confidence interval estimated using 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 1.5, but for the visual test it is around 3.5."}

@@

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating human evaluations of lineups. Surrounding band of the visual test shows the 95 percent confidence interval estimated using 500 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 1.5, but for the visual test it is around 3."}

>>>>

```{r polypower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for non-linear patterns (uniform fitted values only). Main plot shows the power curves estimated using logistic regression, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 1.5, but for the visual test it is around 3.5."}

@@

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 1.5, but for the visual test it is around 3."}

### 2023-01-29 paper_comparison/paper_comparison/paper_comparison.tex
Fix the caption for power cmp

\caption{Comparison of power between different tests for non-linear patterns (uniform fitted values only). Main plot shows the power curves estimated using logistic regression, with dots indicating human evaluations of lineups. Surrounding band of the visual test shows the 95 percent confidence interval estimated using 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 1.5, but for the visual test it is around 3.5.}\label{fig:polypower}
\end{figure}

@@

\caption{Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating human evaluations of lineups. Surrounding band of the visual test shows the 95 percent confidence interval estimated using 500 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 1.5, but for the visual test it is around 3.}\label{fig:heterpower}
\end{figure}

>>>>

\caption{Comparison of power between different tests for non-linear patterns (uniform fitted values only). Main plot shows the power curves estimated using logistic regression, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 1.5, but for the visual test it is around 3.5.}\label{fig:polypower}
\end{figure}

@@

\caption{Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 1.5, but for the visual test it is around 3.}\label{fig:heterpower}
\end{figure}
